Analysis

### 2020-01-17 script/analysis.Rmd
reparar tablas

sink("output/tables/table99.html")
stargazer(list(r99a,r99b,r99c), type= "html",
          covariate.labels = c("Ed.Media", "Ed.Sup.Incomp.", "Ed.Universitaria",
                               "Quintil 2", "Quintil 3","Quintil 2","Quintil 5",
                               "Brecha Percibida"),
          dep.var.labels = c("Brecha Percibida", "Brecha Justa"),
          dep.var.caption  = "Variables dependientes")
sink()

sink("output/tables/table99.html")
stargazer(list(r99a,r99b,r99c), type= "html")
sink()

@@

sink("output/tables/table09.html")
stargazer(list(r09a,r09b,r09c), type= "html",
          covariate.labels = c("Ed.Media", "Ed.Sup.Incomp.", "Ed.Universitaria",
                               "Quintil 2", "Quintil 3","Quintil 2","Quintil 5",
                               "Brecha Percibida"),
          dep.var.labels = c("Brecha Percibida", "Brecha Justa"),
          dep.var.caption  = "Variables dependientes")
sink()

@@

```{r}
load("input/data/processed/clw3.RData")
```

@@

stargazer(reg_year, type="text")

@@

```{r}
int<-plot_model(reg_year, type="int")
int
 ggsave(int,filename = "output/images/int.png",device = "png",width = 20,height = 15,dpi = "retina",units = "cm")

@@

```{r}
options(knitr.kable.NA = '')
kable(desc01,format = "html",
      align = c("l"),
      booktabs=T,
      row.names = F,
      col.names = c("Año","Dimensión","N","Variable/nivel","Media(DS)/%","Min","Max")) %>%
  kable_styling(full_width = F) %>%
  collapse_rows(columns = 1:2,valign = "middle",row_group_label_position = 'stack')

>>>>

sink("output/tables/table99.html")
stargazer::stargazer(list(r99a,r99b,r99c), type= "html",
          covariate.labels = c("Ed.Media", "Ed.Sup.Incomp.", "Ed.Universitaria",
                               "Quintil 2", "Quintil 3","Quintil 2","Quintil 5",
                               "Brecha Percibida"),
          dep.var.labels = c("Brecha Percibida", "Brecha Justa"),
          dep.var.caption  = "Variables dependientes")
sink()

@@

sink("output/tables/table09.html")
stargazer::stargazer(list(r09a,r09b,r09c), type= "html",
          covariate.labels = c("Ed.Media", "Ed.Sup.Incomp.", "Ed.Universitaria",
                               "Quintil 2", "Quintil 3","Quintil 2","Quintil 5",
                               "Brecha Percibida"),
          dep.var.labels = c("Brecha Percibida", "Brecha Justa"),
          dep.var.caption  = "Variables dependientes")
sink()

@@

```{r}
load("input/data/processed/clw3.Rdata")

@@

stargazer::stargazer(reg_year, type="text")

@@

# Revisar - no corre
# int<-sjPlot::plot_model(reg_year, type="int")
# int
#  ggsave(int,filename = "output/images/int.png",device = "png",width = 20,height = 15,dpi = "retina",units = "cm")

@@

```{r}
options(knitr.kable.NA = '')
kableExtra::kable(desc01,format = "html",
      align = c("l"),
      booktabs=T,
      row.names = F,
      col.names = c("Año","Dimensión","N","Variable/nivel","Media(DS)/%","Min","Max")) %>%
  kable_styling(full_width = F) %>%
  collapse_rows(columns = 1:2,valign = "middle",row_group_label_position = 'stack')

#
